Illuminating a Dark Lens : A Type Ia Supernova \\ Magnified by Galaxy Cluster Abell 2744

### 2015-03-24 TABLE/magnifications.tex
implemented most of Chema's comments  and added updated magnification estimates from Bradac/Hoag and Chema to Table 3  and highlighting changes in blue  Note the new sections in the discussion on Redshift Error and System 3.3.

\begin{deluxetable*}{lccp{1.5in}p{2.2in}}
\tablecolumns{5}
\tablecaption{Predicted magnifications for SN \tomas\ from lens models.\label{tab:PredictedMagnifications}}
\tablehead{ \colhead{Model} & \colhead{Best}\tablenotemark{a} & \colhead{Median\tablenotemark{b}} & \colhead{References} & \colhead{Description}}
\startdata
%Sharon         & 2.57$^{+0.19}_{-0.16}$ &   \citealt{Jullo:2007} \\[2mm]
Sharon(v2)   & 2.73 & 2.69$^{+0.14}_{-0.06}$ &   \citealt{Jullo:2007};\citealt{Johnson:2014} & LENSTOOL parametric, strong-lensing based model\\
CATS-SL      & 2.25 & 2.27$^{+0.05}_{-0.04}$ &   \citealt{Jullo:2009,Jauzac:2012} &  LENSTOOL hybrid parametric/free-form, strong lensing based model.\\
CATS-SL+WL   & \nodata & 2.62$^{+0.18}_{-0.18}$ & \citealt{Jullo:2009,Jauzac:2012} &  LENSTOOL hybrid parametric/free-form, strong+weak lensing based model.\\
Jauzac		 & \nodata & 3.37$^{+0.14}_{-0.15}$ &   \citealt{Jauzac:2014,Richard:2014} & Updated version of the CATS-SL model, adds 33 new multiply-imaged galaxies.\\
GLAFIC       & 2.32 & 2.28$^{+0.07}_{-0.11}$ &   \citealt{Oguri:2010,Ishigaki:2015} & Parametric strong-lensing model using the {\tt GLAFIC} code.\tablenotemark{d} \\
Zitrin-NFW   & 2.07 & 2.27$^{+0.23}_{-0.22}$ &   \citealt{Zitrin:2009a} &  Parametric strong-lensing model using PIEMD\tablenotemark{e} profiles for galaxies and NFW\tablenotemark{f} profiles for dark matter halos.\\
Zitrin-LTM   & 2.64 & 2.96$^{+0.77}_{-0.38}$ &   \citealt{Zitrin:2013a} & Parametric strong-lensing model, adopts the Light-Traces-Mass assumption for both the luminous and dark matter.\\
Bradac       & 3.15 & 2.45$^{+0.19}_{-0.16}$ &   \citealt{Bradac:2005,Bradac:2009} & Free-form, strong+weak-lensing based model\\
Williams     & 2.67 & 2.78$^{+2.68}_{-1.14}$ &   \citealt{Liesenborgs:2006,Mohammed:2014} & {\tt GRALE}\tablenotemark{f} : Free-form strong-lensing model using a genetic algorithm.  \\
Merten       & 2.31 & 2.22$^{+0.67}_{-0.19}$ &   \citealt{Merten:2009,Merten:2011} &  SaWLENS, free-form strong+weak lensing based model.\\
Lam			 & \nodata & 2.77$^{+0.36}_{-0.36}$ &   \citealt{Sendra:2014,Lam:2014} & {\tt WSLAP+}\tablenotemark{g} : Free-form strong+weak lensing model using a grid-based method, supplemented by deflections fixed to cluster member galaxies.
\enddata
\tablenotetext{a}{The magnification returned for the optimal version of each model, as independently defined by each lens modeling team.}  
\tablenotetext{b}{Median magnification from 100-600 Monte Carlo realizations of the model. Uncertainties enclose 68\%\ of the realized values.}  
\tablenotetext{c}{{\tt LENSTOOL} : \url{http://projects.lam.fr/repos/lenstool/wiki}}
\tablenotetext{e}{{\tt GLAFIC} : \url{http://www.slac.stanford.edu/~oguri/glafic/}}
\tablenotetext{e}{PIEMD: Pseudo Isothermal Elliptical Mass Distrubition}
\tablenotetext{f}{NFW : Navarro-Frenk-White mass density profile \citep{Navarro:1997}.}
\tablenotetext{g}{{\tt GRALE} : }
\tablenotetext{f}{{\tt WSLAP+} : Weak and Strong Lensing Analysis Package plus member galaxies}
\end{deluxetable*}

>>>>

\begin{deluxetable*}{lccp{1.5in}p{2.2in}}
\tablecolumns{5}
\tablecaption{Predicted magnifications for SN \tomas\ from lens models.\label{tab:PredictedMagnifications}}
\tablehead{ \colhead{Model} & \colhead{Best}\tablenotemark{a} & \colhead{Median\tablenotemark{b}} & \colhead{References} & \colhead{Description}}
\startdata
%Sharon         & 2.57$^{+0.19}_{-0.16}$ &   \citealt{Jullo:2007} \\[2mm]
Sharon(v2)   & 2.73 & 2.69$^{+0.14}_{-0.06}$ &   \citealt{Jullo:2007};\citealt{Johnson:2014} & LENSTOOL parametric, strong-lensing based model\\
CATS-SL      & 2.25 & 2.27$^{+0.05}_{-0.04}$ &   \citealt{Jullo:2009,Jauzac:2012} &  LENSTOOL hybrid parametric/free-form, strong lensing based model.\\
CATS-SL+WL   & \nodata & 2.62$^{+0.18}_{-0.18}$ & \citealt{Jullo:2009,Jauzac:2012} &  LENSTOOL hybrid parametric/free-form, strong+weak lensing based model.\\
Jauzac		 & \nodata & 3.37$^{+0.14}_{-0.15}$ &   \citealt{Jauzac:2014,Richard:2014} & Updated version of the CATS-SL model, adds 33 new multiply-imaged galaxies.\\
GLAFIC       & 2.32 & 2.28$^{+0.07}_{-0.11}$ &   \citealt{Oguri:2010,Ishigaki:2015} & Parametric strong-lensing model using the {\tt GLAFIC} code.\tablenotemark{d} \\
Zitrin-NFW   & 2.07 & 2.27$^{+0.23}_{-0.22}$ &   \citealt{Zitrin:2009a} &  Parametric strong-lensing model using PIEMD\tablenotemark{e} profiles for galaxies and NFW\tablenotemark{f} profiles for dark matter halos.\\
Zitrin-LTM   & 2.64 & 2.96$^{+0.77}_{-0.38}$ &   \citealt{Zitrin:2013a} & Parametric strong-lensing model, adopts the Light-Traces-Mass assumption for both the luminous and dark matter.\\
Bradac(v1)   & 3.15 & 2.45$^{+0.19}_{-0.16}$ &   \citealt{Bradac:2005,Bradac:2009} & {\tt SWUnited} : Free-form, strong+weak-lensing based model\\
Bradac(v2)   & 2.23 & 2.20$^{+0.03}_{-0.01}$ &   \citealt{Bradac:2005,Bradac:2009} & \change{Updated version of the {\tt SWUnited} model with new strong-lensing constraints from HFF imaging.}\\
Williams     & 2.67 & 2.78$^{+2.68}_{-1.14}$ &   \citealt{Liesenborgs:2006,Mohammed:2014} & {\tt GRALE}\tablenotemark{g} : Free-form strong-lensing model using a genetic algorithm.  \\
Merten       & 2.31 & 2.22$^{+0.67}_{-0.19}$ &   \citealt{Merten:2009,Merten:2011} &  SaWLENS, free-form strong+weak lensing based model.\\
Lam			 & \nodata & 2.77$^{+0.36}_{-0.36}$ &   \citealt{Sendra:2014,Lam:2014} & {\tt WSLAP+}\tablenotemark{h} : Free-form model strong-lensing using a grid-based method, supplemented by deflections fixed to cluster member galaxies.\\
Diego\tablenotemark{i}			 & \nodata & 2.10$^{+0.36}_{-0.36}$ &   \citealt{Sendra:2014,Lam:2014} & \change{Alternative implementation of the {\tt WSLAP+}\tablenotemark{h} model, using a different set of strong-lensing constraints and redshifts.}
\enddata
\tablenotetext{a}{The magnification returned for the optimal version of each model, as independently defined by each lens modeling team.}  
\tablenotetext{b}{Median magnification from 100-600 Monte Carlo realizations of the model. Uncertainties enclose 68\%\ of the realized values.}  
\tablenotetext{c}{{\tt LENSTOOL} : \url{http://projects.lam.fr/repos/lenstool/wiki}}
\tablenotetext{d}{{\tt GLAFIC} : \url{http://www.slac.stanford.edu/~oguri/glafic/}}
\tablenotetext{e}{PIEMD: Pseudo Isothermal Elliptical Mass Distrubition}
\tablenotetext{f}{NFW : Navarro-Frenk-White mass density profile \citep{Navarro:1997}.}
\tablenotetext{g}{{\tt GRALE} : }
\tablenotetext{h}{{\tt WSLAP+} : Weak and Strong Lensing Analysis Package plus member galaxies \change{(Note: no weak-lensing constraints used for Abell 2744)}}
\tablenotetext{i}{\change{No uncertainty estimates were available for the Diego implementation of the {\tt WSLAP+} model, so we adopt the uncertainties from the Lam model.}}
\end{deluxetable*}

### 2015-03-24 snTomas.tex
implemented most of Chema's comments  and added updated magnification estimates from Bradac/Hoag and Chema to Table 3  and highlighting changes in blue  Note the new sections in the discussion on Redshift Error and System 3.3.

A spectrum of SN \tomas\ was collected with the ACS G800L grism on
2014 June 4 and 7, when the SN was very near to its peak brightness.
The observations -- listed at the bottom of Table~\ref{tab:Photometry}
-- used 5 HST orbits from the FrontierSN program for a total
spectroscopic exposure time of $\sim$10 ksec.  The grism data were
processed and the target spectrum was extracted using the custom
pipeline employed by the Grism Lens Amplified Survey from Space
program (GLASS; PI:Treu, PID:13459). \textcolor{red}{Is there a
citation for this? or more to say here?}

@@

Table~\ref{tab:PredictedMagnifications} lists the 11 models, giving
for each one the predicted magnification and uncertainty for a source
at $z=1.31\pm0.01$ and at the position of \tomas.  These
models represent a broad sampling of the techniques and assumptions
that can be applied to the modeling of mass distributions in galaxy
clusters. A rigorous comparison of these disparate lens modeling
techniques is beyond the scope of this work. Table 10 includes a brief
description of each model, but for a complete discussion of the
methodology the reader is referred to the listed references.

@@

@@

Seven of the mass models evaluated here are constrained only using
strong-lensing features such as multiply-imaged background galaxies
and highly magnified arcs.  There are now $\sim$150 known lensed
images behind Abell 2744 \citep{Jauzac:2014c}, but SN \tomas\ is
located several arcseconds outside the core region of the cluster
where these multiply-imaged galaxies are found.  Therefore these seven
``strong-lensing only'' models must necessarily rely on extrapolations
to provide a prediction for the SN \tomas\ magnification.  If the true
cluster density profile for Abell 2744 happens to be truncated -- with
a sharp drop right at the edge of this core strong-lensing region --
then these seven models might well overestimate the mass interior to
the \tomas\ position, and thus systematically overestimate the
magnification.

The other four models in our comparison set also use the strong
lensing constraints from the core region, but also utilize weak
lensing measurements to provide additional constraints on the mass
distribution farther from the cluster core.  The signal from weak
lensing relies on a large sample of background galaxies, so this
constraint operates principally at separations more than 1\arcmin from
the cluster core.  At a projected separation of $\sim40\arcsec$,
SN \tomas\ falls in between the strong- and weak-lensing regimes, and
one would expect that models incorporating both of those constraints
would be less susceptible to the systematic bias of a truncated mass
profile.  The lowest magnification estimate in our sample (from the
Merten model) is among this sub-sample.  However, we find that
collectively these four strong+weak models (shown as diamonds in
Figure~\ref{fig:lensingtest}) exhibit the same propensity to
overestimate the magnification along this line of sight.  Thus, a
sudden change in the mass profile outside the strong lensing region is
not a likely explanation for this small systematic bias.

@@

If the redshift of the SN derived in Section~\ref{sec:Spectroscopy}
were incorrect, then one would derive a different value for the
magnification, both from the SN measurement and the lens model
predictions.  Conceivably, this could resolve the tension between the
measurement and the models.  It is often the case in SN surveys that
redshifts are assigned based on a host galaxy association, typically
inferred from the projected separation between the SN and nearby
galaxies.  In this case the redshift evidence comes from the SN
itself, and we find a consistent redshift from both the SN spectrum
(Section~\ref{sec:SpecRedshift}) and the light curve
Section~\ref{sec:PhotometricClassification}, which are both within the
$1\sigma$ range of the photometric redshift for the nearest detected
galaxy: $z=1.5\pm0.2$. This appears to be a solid and self-consistent
picture, so the evidence strongly disfavors any redshift that is
significantly different from $z=1.3$.

We have adopted the spectroscopic redshift of $z=1.31\pm0.01$ for the
magnification comparison.  Spectroscopic redshifts are generally more
precise and accurate than those derived from photometric
observations \citep{Rodney:2010b,Kessler:2010,Sako:2011}.  However, in
this case the spectrum is limited to the rest-frame near-UV
wavelengths, where the available SN spectral template libraries are
more limited than at optical wavelengths.  If we use the photometric
redshift of $z=1.35\pm0.02$ instead, then the measured magnification
is reduced. \footnote{By increasing the redshift, the SN is presumed
to be at a greater distance, so to first order one would be expect it
to appear slightly fainter (larger distance modulus). If the distance
modulus inferred from the light curve fit remained constant, this
would drive the inferred magnification to a higher value.  However,
the intrinsic peak brightness as derived from light curve fitting is
more strongly affected by the covariance between redshift, color, and
light curve width.  In this case, these effects drive the distance
modulus to a larger value at $z=1.35$ that is closer to the unlensed
population than we get at $z=1.31$.}  From the SALT2 fitter we derive
$\mu_{\rm SALT2}=1.80\pm0.30$ and from MLCS2k2 we get $\mu_{\rm
MLCS2k2}=1.83\pm0.17$.  The lens models are also shifted, and they
uniformly move in the opposite direction, to magnification values that
are {\it larger}, by $\sim1$\%.  Thus, shifting the SN to the
photometric redshift of $z=1.35$ only serves to (slightly) exacerbate
the tension between the observations and models.

@@

We have speculated on the possible origin of this systematic bias,
evaluating three possible causes:

\begin{enumerate}
\item The close proximity of a cluster member galaxy is leading to a
biased magnification, because that galaxy's M/L is atypical.
\item The models are limited by a scarcity of strong lensing constraints
\item The cluster mass profile exhibits a sudden change outside of the core
strong-lensing region, where we lack multiply-imaged background
sources to constrain it. 
\end{enumerate}

\noindent None of these three explanations is completely
satisfactory.  For each of these scenarios, we would expect that
certain subsets of the available lens models would be less sensitive
to the proposed systematic bias.  However, the small discrepancy
between the predicted and observed lensing magnification is persistent
when we bifurcate the sample of lens models according to methodology
(parametric vs. free-form), number of strong-lensing constraints (pre-
vs post-HFF), and scope of lensing constraints (strong-lensing only
vs. strong+weak).  We do not have any definitive explanation for this
magnification discrepancy.

@@

We are very pleased to thank the Hubble Frontier Fields team at STScI
for their substantial efforts to make the HFF program successful.  In
particular, thanks are due to Matt Mountain for the allocation of
discretionary orbits for the HFF program; to Jennifer Lotz, Norman
Grogin and Patricia Royle for accommodations in strategy and
implementation to make the FrontierSN program possible; and to Dan Coe
for curating the excellent and accessible lens model comparison tools.
We also must thank the CLASH team, led by Marc Postman, for
observations, catalogs, and high level science products that were of
significant value for this analysis.

@@

>>>>

A spectrum of SN \tomas\ was collected with the ACS G800L grism on
2014 June 4 and 7, when the SN was very near to its peak brightness.
The observations -- listed at the bottom of Table~\ref{tab:Photometry}
-- used 5 HST orbits from the FrontierSN program for a total
spectroscopic exposure time of $\sim$10 ksec.  The grism data were
processed and the target spectrum was extracted using a custom
pipeline \citep{Brammer:2012}, which was developed for the 3D-HST
program (PI:Van Dokkum; PID:12177, 12328) and also used by the Grism
Lens Amplified Survey from Space (GLASS; PI:Treu; PID:13459).

@@

Table~\ref{tab:PredictedMagnifications} lists the 11 models, giving
for each one the predicted magnification and uncertainty for a source
at $z=1.31\pm0.01$ and at the position of \tomas.  These models
represent a broad sampling of the techniques and assumptions that can
be applied to the modeling of mass distributions in galaxy clusters. A
rigorous comparison of these disparate lens modeling techniques is
beyond the scope of this work. Table~\ref{tab:PredictedMagnifications}
includes a brief description of each model, but for a complete
discussion of the methodology the reader is referred to the listed
references.

@@

\change{
\subsection{Misidentification of System 3}
\label{sec:MisidentificationOfSystem3}
}
\change{
It is important to note that in regards to the impact on this
particular sight-line, not all strong-lensing constraints are equal.
An error in the association of multiple images or 
in the redshift of a multiply-imaged galaxy would have a
more significant impact if that system has a projected position
close to our SN sight-line.  It happens that there is one such system,
for which the position of a multiple image near SN \tomas\ is presently disputed.  
}

\change{
This multiply-imaged galaxy was originally labeled as {\it System 3}
in \citet{Merten:2011}.  As shown in Figure~\ref{fig:System3}, it is
stretched into two adjacent arcs northwest of the cluster core (images
3.1 and 3.2), with a third image on the western edge of the
strong-lensing region (image 3.3 at 00:14:18.595,
-30:23:58.42).  \citet{Richard:2014} echoed this initial
identification in producing the {\tt CATS} models, which we cite in
Table~\ref{tab:PredictedMagnifications} and
Figure~\ref{fig:lensingtest}.  In developing the {\tt Sharon-v2}
models, \citet{Johnson:2014} provided a secure spectroscopic
constraint of $z=3.98\pm0.02$ for this system, based on a spectrum of
the combined 3.1+3.2 source. The identification of the original image
3.3 has been called into question by two independent analyses.  Using
HFF imaging data, \citet{Lam:2014} suggested an alternative third
image for this system roughly 8\arcsec\ to the south, which we will
call \33p\ (00:14:18.39, -30:24:06.53).
However, \citeauthor{Lam:2014} rejected this possibility based on a
difference in colors between \33p\ and images 3.1 and 3.2.  In
contrast, \citeauthor{Jauzac:2014c} argue that the position \33p\
is correct, and find that reassigning this multiple image results in a
tighter model reconstruction for the locations of other
multiply-imaged systems in the vicinity.
}

\change{
Resolving the identification of this single multiply-imaged galaxy
could be an important component in resolving the magnification
discrepancy, though it is unlikely to completely remove the tension.
It is true that the model that reassigns the position to \33p\
({\tt Jauzac}) is also the one with the largest deviation from our
observed $\mu$ value.  However, the bias is still present even if we
remove that model and only consider models using the original position
3.3.  
}

@@

Eight of the mass models evaluated here are constrained only using
strong-lensing features such as multiply-imaged background galaxies
and highly magnified arcs.  There are now $\sim$150 known lensed
images behind Abell 2744 \citep{Jauzac:2014c}, but SN \tomas\ is
located several arcseconds outside the core region of the cluster
where these multiply-imaged galaxies are found.  Therefore these seven
``strong-lensing only'' models must necessarily rely on extrapolations
to provide a prediction for the SN \tomas\ magnification.  If the true
cluster density profile for Abell 2744 happens to be truncated -- with
a sharp drop right at the edge of this core strong-lensing region --
then these seven models might well overestimate the mass interior to
the \tomas\ position, and thus systematically overestimate the
magnification.

The other three models in our comparison set also use the strong
lensing constraints from the core region, but additionally utilize weak
lensing measurements to provide additional constraints on the mass
distribution farther from the cluster core.  The signal from weak
lensing relies on a large sample of background galaxies, so this
constraint operates principally at separations more than 1\arcmin from
the cluster core.  At a projected separation of $\sim40\arcsec$,
SN \tomas\ falls in between the strong- and weak-lensing regimes, and
one would expect that models incorporating both of those constraints
would be less susceptible to the systematic bias of a truncated mass
profile.  The lowest magnification estimate in our sample (from the
Merten model) is among this sub-sample.  However, we find that
collectively these three strong+weak models (shown as diamonds in
Figure~\ref{fig:lensingtest}) exhibit the same propensity to
overestimate the magnification along this line of sight.  Thus, a
sudden change in the mass profile outside the strong lensing region is
not a likely explanation for this small systematic bias.

@@

\change{
If the redshift of the SN derived in Section~\ref{sec:Spectroscopy}
were incorrect, then one would derive a different value for the
magnification, both from the SN measurement and the lens model
predictions.  Conceivably, this could resolve the tension between the
measurement and the models.  It is often the case in SN surveys that
redshifts are assigned based on a host galaxy association, typically
inferred from the projected separation between the SN and nearby
galaxies.  In this case the redshift evidence comes from the SN
itself, and we find a consistent redshift from both the SN spectrum
(Section~\ref{sec:SpecRedshift}) and the light curve
Section~\ref{sec:PhotometricClassification}, which are both within the
$1\sigma$ range of the photometric redshift for the nearest detected
galaxy: $z=1.5\pm0.2$. This appears to be a solid and self-consistent
picture, so the evidence strongly disfavors any redshift that is
significantly different from $z=1.3$.
}

\change{
We have adopted the spectroscopic redshift of $z=1.31\pm0.01$ for the
magnification comparison.  Spectroscopic redshifts are generally more
precise and accurate than those derived from photometric
observations \citep{Rodney:2010b,Kessler:2010,Sako:2011}.  However, in
this case the spectrum is limited to the rest-frame near-UV
wavelengths, where the available SN spectral template libraries are
more limited than at optical wavelengths.  If we use the photometric
redshift of $z=1.35\pm0.02$ instead, then the measured magnification
is reduced.\footnote{By increasing the redshift, the SN is presumed to
be at a greater distance, so to first order one would be expect it to
appear slightly fainter (larger distance modulus). If the distance
modulus inferred from the light curve fit remained constant, this
would drive the inferred magnification to a higher value.  However,
the light curve fitting is more strongly affected by the covariance
between redshift, color, and light curve width.  In this case, these
effects drive the distance modulus to a larger value at $z=1.35$,
resulting in a smaller value of the observed magnification $\mu$.}
From the SALT2 fitter we derive $\mu_{\rm SALT2}=1.80\pm0.30$ and from
MLCS2k2 we get $\mu_{\rm MLCS2k2}=1.83\pm0.17$.  The lens models are
also shifted, and they uniformly move in the opposite direction, to
magnification values that are {\it larger} than at $z=1.31$, by
$\sim1$\%.  Thus, shifting the SN to the photometric redshift of
$z=1.35$ only serves to (slightly) exacerbate the tension between the
observations and models.
}

@@

We have speculated on the origin of this systematic bias,
evaluating five possible causes:

\begin{enumerate}
\item The close proximity of a cluster member galaxy is leading to a
biased magnification, because that galaxy's M/L is atypical.
\item The models are limited by a scarcity of strong lensing constraints
\item The cluster mass profile exhibits a sudden change outside of the core
strong-lensing region, where we lack multiply-imaged background
sources to constrain it. 
\item \change{The redshift assigned to SN \tomas\ is in error.}
\item \change{SN \tomas\ is not a normal Type Ia SN.}
\end{enumerate}

\noindent The first three of these take on the discrepancy from 
the lens modeling side, but none are completely satisfactory. For each
of these scenarios, we would expect that certain subsets of the
available lens models would be less sensitive to the proposed
systematic bias.  However, the small discrepancy between the predicted
and observed lensing magnification is persistent when we bifurcate the
sample of lens models according to methodology (parametric
vs. free-form), number of strong-lensing constraints (pre- vs
post-HFF), and scope of lensing constraints (strong-lensing only
vs. strong+weak). Thus, comparison of the available models does not
provide any definitive explanation for this magnification tension.

\change{
The last two possible explanations presume an error in the
interpretation of the available SN data.  We reject the possibility
that a redshift error is the primary cause of the discrepancy, as the
redshift evidence is derived principally from the SN itself and not
from the host galaxy. A value of $z\sim1.3$ is well supported by both
the spectroscopic and photometric SN data, and changing the redshift
within the constraints of these complementary observations only serves
to increase the tension between the observed and predicted
magnifications.
}

\change{
Finally, we have considered whether the SN could be
mis-classified. Once again the combination of spectroscopic and
photometric evidence strongly supports our classification of
SN \tomas\ as a normal Type Ia SN.  The most plausible
mis-classification would be that the object is a peculiar Type Ia of
the SN 2006bt-like sub-class.  We find this possibility to be 
 \textcolor{red}{TODO: summarize the 06bt misclassification discussion}
}

@@

We are p

We thank the Hubble Frontier Fields team at STScI
for their substantial efforts to make the HFF program successful.  In
particular, thanks are due to Matt Mountain for the allocation of
discretionary orbits for the HFF program; to Jennifer Lotz, Norman
Grogin and Patricia Royle for accommodations in strategy and
implementation to make the FrontierSN program possible; and to Dan Coe
for curating the excellent and accessible lens model comparison tools.
We also must thank the CLASH team, led by Marc Postman, for
observations, catalogs, and high level science products that were of
significant value for this analysis.

@@

J.M.D acknowledges support of the consolider project CAD2010-00064 and
AYA2012-39475-C02-01 funded by the Ministerio de Economia y
Competitividad.
